Exploring Bounds

### 2015-04-26 draft.tex
draft finished, revise and then submit

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{verbatim}
\usepackage{graphicx}
%\usepackage{caption}
%\usepackage{subfig}
%\usepackage{enumitem}

@@

\newtheorem{theorem}{Theorem}
\numberwithin{theorem}{subsection}

\newtheorem{lemma}{Lemma}
\numberwithin{lemma}{subsection}

\theoremstyle{definition}
\newtheorem{exmp}{Example}
\numberwithin{exmp}{subsection}

\theoremstyle{definition}
\newtheorem{defn}{Definition}
\numberwithin{defn}{subsection}

\theoremstyle{definition}
\newtheorem{claim}{Claim}
\numberwithin{claim}{subsection}

@@

For arbitrary $n$ and $d$, it is difficult to find $A_q(n,d)$ and $B_q(n,d)$ exactly.
 In lecture, we have considered upper bounds---Sphere Packing, Singleton, and Greismer---as well as
lower bounds---Gilbert and Varshamov---on these values.  The purpose of this
paper is to take a survey of other well-known bounds in the literature that we have not discussed.  
In the first part of the paper, we will consider the Plotkin Upper bound, 
the Elias Upper bound, and the Linear Programming Upper Bound.  In the second part of the paper, we will consider asymptotic versions
of Singleton, Plotkin, Hamming, and Elias.  (I am very certain that I won't get to discuss all of these bounds, but I am currently unsure how much space each discussion will take up so I've
listed all that I am considering.)  For each bound, we will consider its proof as well
as related examples.  Lastly, in the final part we will consider lexicodes, an interesting subset of linear codes that meet the Gilbert Bound.

Some implementation specific details: for the Linear Programming bound, I will introduce basic linear programming concepts and as well as the Krawtchouck polynomials.  For the 
Asymptotic Hamming bound I will introduce the Hilbert entropy function.

@@

\subsection{Plotkin Upper Bound}
%Plotkin
%talk about importance
%define it
%prove it
%work out some examples

@@

Using MATLAB, I sought to visualize how the Plotkin and Sphere Packing bounds compare.  To do so, I plotted their values over $8\le n \le 25$, with $d>rn$.

In order to turn my discrete 3d data into a smooth mesh surface, I needed a mechanism to smooth out my data.  My solution was to utilize Delaunay triangulation.

It is also interesting to consider a broader picture of how Plotkin compares to Sphere Packing, Greismer, and other bounds we have considered in lecture.  Below is a graph comparing rates of codes versus the Sphere Packing and Plotkin bounds
that we can calculate for those values for different values of q.

\begin{comment}
\begin{figure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{plotkin_q2.png}
  \caption{1a}
  \label{fig:sfig1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{plotkin_q3.png}
  \caption{1b}
  \label{fig:sfig2}
\end{subfigure}
\caption{plots of....}
\label{fig:fig}
\end{figure}
\end{comment}

@@

Another upper bound on $A_q(n,d)$ is due to Elias in 1960.  The Elias bound is generally weaker than other bounds we have discussed, but is important because of the asymptotic
form of this bound that we will discuss towards the end of this paper.

@@

@@

@@

@@

 For $w=1$, 
we get $A_2(13,5)\le \frac{.5\cdot13\cdot5}{1 - 2\cdot.5\cdot13 + .5\cdot13\cdot5}\cdot\frac{2^{13}}{V_q(13,1)} = \frac{32.5}{1-13+32.5}\cdot\frac{2^{13}}{1+13} = 927$;
similarly $A_2(14,6)\le \frac{.5\cdot14\cdot6}{1 - 2\cdot.5\cdot14 + .5\cdot14\cdot6}\cdot\frac{2^{14}}{V_q(14,1)} = \frac{42}{1-14+42}\cdot\frac{2^{14}}{1+14} = 1581$;

@@

Consequently, for our asymptotic bounds, we are interested in the largest
possible rate for a family of codes over $\mathbb{F}_q$ of lengths going to
infinity with a relative distance of some constant $\delta$.  In other words, we consider the equation:

@@

For the rest of this section, we will consider some bounds on $A_q(n,\delta n)$

@@

\begin{exmp}

\subsection{Asymptotic Plotkin Bound}

\section{Lexicodes}
We end our discussion on bounds with an interesting class of binary linear codes
called lexicodes, short for lexicographic codes.  Lexicodes are linear and meet the Gilbert bound; we will discuss the former and prove the latter.  Note that for this discussion we are 
solely working in $\mathbb{F}_2$.

We construct the lexicode $\mathcal{L}$ of length $n$ and minimum distance $d$ using a basic greedy algorithm as follows.  First, order all $n$-tuples in an array $A$ in lexicographic order:
$A[0] = 0\cdots000$, $A[1]=0\cdots001$, $A[2]0\cdots010$, $A[3]=0\cdots011$, \ldots, $A[2^n-1] = 1\cdots111$.  Put the first vector from  $A$ (always the $\mathbf{0}$ vector) in $\mathcal{L}$.  Next, find the first vector $\mathbf{x}$
of weight $d$ in the lexicographic ordering, and put it in $\mathcal{L}$.  Then, find the next vector in the lexicographic ordering in $A$ whose distance from each vector in $\mathcal{L}$ is 
$d$ or more and add it to $\mathcal{L}$.  Repeat this process until you have scanned through all of $A$ once.

@@

\begin{enumerate}
\item $\mathcal{L}$ is a linear code and the vectors $\mathbf{c}_{2^i}$ are a basis of $\mathcal{L}$.  
\item After $\mathbf{c}_{2^i}$ is chosen, the next $2^i -1$ vectors can be rewritten as $\mathbf{c}_1 + \mathbf{c}_{2^i}$, $\mathbf{c}_2 + \mathbf{c}_{2^i}$, $\ldots$, 
$\mathbf{c}_{2^i -1} + \mathbf{c}_{2^i}$.
\item Let $\mathcal{L}_i = \{\mathbf{c}_0,\mathbf{c}_1,\ldots,\mathbf{c}_{2^i -1}\}$.  Then $\mathcal{L}_i$ is an $[n,i,d]$ linear code.

@@

Though I won't prove this, it is not difficult to see that $1.$ and $3.$ follow from $2.$    In $2.$, we are showing that all codewords in the lexicode are simply linear combinations of 
the $c_{2^i}$ codewords, hence making the $c_{2^i}$ codewords a basis for the code.

@@

@@

Notice that this is simply the even weight vectors.  In fact, it is true that
for any $q$.
THIS IS THE EVEN WEIGHT CODE! prove it.

@@

Some notable codes we have discussed in class are in fact lexicodes.
[REFERENCE]

We can prove a basic property of binary Lexicodes.  First, though, we
need an important definition.

@@

We have used the idea of nim-sums and zero-sums throughout the course, but instead we have
referred to this notion in terms being even-like or odd-like.  This is the
exact same notion, only in different terms.

@@

\begin{proof}
We will prove this by inducting on $n$.  In the base case of $n=1$,
$\mathcal{L}=\{0\}$, which is trivially zero-sum.  Assume that for the
lexicode of length $n$, which we will denote $\mathcal{L}(n)$, all codewords are zero-sum.  Now, we must show that all
the codewords in $\mathcal{L}(n+1)$ are zero-sum as well.  First, note that all
codewords in $\mathcal{L}(n)$ are also in $\mathcal{L}(n+1)$, except with an
extra leading zero.  By our assumption, these codewords are still zero-sum, as
adding a zero in front will not change the nim-sum calculation.
Now, we must show that any vector we can add to this set as proscribed by our
algorithm must necessarily be a zero-sum vector as well.
\end{proof}

For example, the binary lexicodes with $d$=3 and $n=2^m-1$ are the binary hamming codes.  It can be quite
tedious to compute and confirm something like this by hand, so I wrote a short C++ program that implements the Lexicode algorithm as described above.

\begin{exmp}
Let $n=7$, $d=3$.  We find $\mathcal{L}= \{0000000,000111,  \}$
\end{exmp}

Need to talk about paper
http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=1057187

%First explore linear programming bound
Asymptotic singleton, include 2 examples
Asymptotic plotkin, some examples
draw graph
Asymptotic hamming
	define hilbert, prove 135,136, define vq(n,a),
	black box 2.10.3, prove 2.10.5

Table of common$a_q(n,d)$ values
Recall basic theory: thm 2.1.2, 2.1.6

Sections

Elias
talk about importance
define it
prove two lemmas that do the heavy lifting
easy proof to finish it off
work out some examples

Linear Programming Bound
talk about importance
define it
prove it
work out some examples

Note existence of two lower bounds, say we talked about them in class

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{enumerate}
%\usepackage{figure}

%\usepackage{caption}
%\usepackage{subfig}
%\usepackage{enumitem}

@@

\theoremstyle{plain}
  \newtheorem{theorem}{Theorem}[section]
  \newtheorem{prop}[theorem]{Proposition}
  \newtheorem{cor}[theorem]{Corollary}
  \newtheorem{lemma}[theorem]{Lemma}
  \newtheorem{claim}[theorem]{Claim}
\theoremstyle{definition}
  \newtheorem{defn}[theorem]{Definition}
  \newtheorem{exmp}[theorem]{Example}
  \newtheorem{obs}[theorem]{Observation}
  \newtheorem{remark}[theorem]{Remark}
  \newtheorem{construction}[theorem]{Construction}

@@

For arbitrary $n$ and $d$, it is difficult to find $A_q(n,d)$ and $B_q(n,d)$ exactly.
 In lecture, we have considered upper bounds---Sphere Packing, Singleton, and Greismer---as well as
lower bounds---Gilbert and Varshamov---on these values.  The purpose of this
paper is to take a survey of other well-known bounds in the literature that we have not discussed.  
In the first part of the paper, we will consider the Plotkin Upper bound, 
the Elias Upper bound.  In the second part of the paper, we will consider the asymptotic versions of the Singleton, Plotkin, and Elias bounds.  Lastly, in the final part we will consider lexicodes, an interesting subset of linear codes that meet the Gilbert Bound.

@@

\subsection{Plotkin Upper Bound}

@@

Using MATLAB, I sought to visualize how the Plotkin and Sphere Packing bounds compare.  To do so, I plotted their values over $8\le n \le 25$, with $d>rn$.  Below is the case
of $q=2$; I found similar but more smoothed out results for higher values of $q$ (see submission folder).

\begin{figure}[ht]
\includegraphics[width=.8\linewidth]{plotkin_q2.png}
\caption{Plotkin and Sphere Packing bounds for $n,d\in[8,25]$}
\end{figure}
I also thought it would be interesting to visualize how the Plotkin bound and Sphere Packing bounds operate as a function of $n$ and $d$.  Given various values of $n$ and $d$, I plotted the resulting bound, 
and then used Delaunay triangulation [REFERENCE] to turn the discrete 3D data into a smooth mesh surface.  (See Sphere Packing data on next page).

\begin{figure}
\centering
\begin{minipage}[b]{0.45\linewidth}
\includegraphics[width=1.4\linewidth]{plotkin.png}
\label{fig:minipage1}
\end{minipage}
\quad
\begin{minipage}[b]{0.45\linewidth}
\includegraphics[width=1.4\linewidth]{plotkin_2.png}
\label{fig:minipage2}
\end{minipage}
\caption{Two different perspectives of the same graph, the Plotkin Bound for $q$=2, $n,d\in[6,40]$ }
\end{figure}

\begin{figure}
\centering
\begin{minipage}[ht]{0.45\linewidth}
\includegraphics[width=1.4\linewidth]{sp_1.png}
\label{fig:minipage1}
\end{minipage}
\quad
\begin{minipage}[ht]{0.45\linewidth}
\includegraphics[width=1.4\linewidth]{sp_2.png}
\label{fig:minipage2}
\end{minipage}
\caption{Two different perspectives of the same graph, the Sphere Packing Bound for $q$=2, $n,d\in[6,40]$ }
\end{figure}

@@

Another upper bound on $A_q(n,d)$ is due to Elias in 1960.  The Elias bound is generally weaker than other bounds we have discussed, but is important because of the asymptotic
form that it generates.

@@

The proof of this lemma uses a very similar technique to that used in our proof of the Plotkin bound. Just as before, given an $(n,K,d)$ code $\mathcal{C}$, the proof considers
the $K \times n$ matrix $\mathcal{M}$ whose rows are the codewords of $\mathcal{C}$.  Using this matrix, the proof takes the expression $K(K-1)d$ and shows through a number of equation manipulations
that it is less than or equal the expression $K^2 w\left( 2 - \frac{w}{rn}\right )$.  Two key tools for the proof are the Cauchy-Schwartz inequality, and the relationship between 
the sum of the distances between all pairwise codewords and the sums of the $n_{i,\alpha}$ values in the columns of $\mathcal{M}$.

As an aside: the second lemma, stated below, uses the notation $V_q(n,a)$ to denote the number of vectors in a sphere of radius $a$ in $\mathbb{F}_q^n$.  This is a concept 
that we became very familiar with this semester in our discussions of the Sphere Packing and Gilbert bounds.

@@

The proof of this lemma begins by considering the intersection between a sphere of radius w centered at $\mathbf{0}$, and the special vector $x\in \mathbb{F}_q^n$ added to $\mathcal{C}$ such that the intersection
is maximal.  The important step is noticing that this value is greater than or equal to the sum over all vectors $y\in\mathbb{F}_q^n$ of that same sphere of radius $w$, intersected with 
$y+\mathcal{C}$, all divided by $q^n$.  The proof then uses sum manipulations to find a relationship between our original expression and $\frac{1}{q^n}V_q(n,w)M$.

@@

The proof of this theorem, though omitted, follows almost directly from the previous two lemmas.

@@

 For $w=1$, 
we get $A_2(13,5)\le \frac{.5\cdot13\cdot5}{1 - 2\cdot.5\cdot13 + .5\cdot13\cdot5}\cdot\frac{2^{13}}{V_q(13,1)} = \frac{32.5}{1-13+32.5}\cdot\frac{2^{13}}{1+13} = 927$;
similarly $A_2(14,6)\le \frac{.5\cdot14\cdot6}{1 - 2\cdot.5\cdot14 + .5\cdot14\cdot6}\cdot\frac{2^{14}}{V_q(14,1)} = \frac{42}{1-14+42}\cdot\frac{2^{14}}{1+14} = 1581$.

For $w=2$, 
we get  $A_2(13,5)\le \frac{.5\cdot13\cdot5}{4 - 2\cdot2\cdot.5\cdot13 + .5\cdot13\cdot5}\cdot\frac{2^{13}}{V_q(13,2)} = \frac{32.5}{4-26+32.5}\cdot\frac{2^{13}}{1+13+78} = 275$;
similarly $A_2(14,6)\le \frac{.5\cdot14\cdot6}{4 - 2\cdot2\cdot.5\cdot14 + .5\cdot14\cdot6}\cdot\frac{2^{14}}{V_q(14,2)} = \frac{42}{4-28+42}\cdot\frac{2^{14}}{1+14+91} = 360$.

For $w=3$, 
we get  $A_2(13,5)\le \frac{.5\cdot13\cdot5}{9 - 2\cdot3\cdot.5\cdot13 + .5\cdot13\cdot5}\cdot\frac{2^{13}}{V_q(13,3)} = \frac{32.5}{9-39+32.5}\cdot\frac{2^{13}}{1+13+78+286} = 281$;
similarly $A_2(14,6)\le \frac{.5\cdot14\cdot6}{9 - 2\cdot3\cdot.5\cdot14 + .5\cdot14\cdot6}\cdot\frac{2^{14}}{V_q(14,3)} = \frac{42}{9-42+42}\cdot\frac{2^{14}}{1+14+91+ 364} = 162$.

For $w=4$,
in the case of $A_2(13,5)$, the first denominator is less than zero, and thus we cannot apply the bound; $A_2(14,6)$ still works, however.  
$A_2(14,6)\le \frac{.5\cdot14\cdot6}{16 - 2\cdot4\cdot.5\cdot14 + .5\cdot14\cdot6}\cdot\frac{2^{14}}{V_q(14,4)} = \frac{42}{16-56+42}\cdot\frac{2^{14}}{1+14+91+ 364+1001} = 233$.

Thus the best upper bound from the Elias Bound for $A_2(13,5)=A_2(14,6)=162$.

@@

For our asymptotic bounds, we are interested in the largest
possible rate for a family of codes over $\mathbb{F}_q$ of lengths going to
infinity with a relative distance of some constant $\delta$.  In other words, we consider the equation:

@@

For the rest of this section, we will consider two bounds on $A_q(n,\delta n)$

@@

\subsection{Asymptotic Plotkin Bound}
The Asymptotic Plotkin Bound gives a small improvement on the Asymptotic Single Bound.

\begin{theorem}
Let $r=1-q$.  Then 
\begin{equation*}
\alpha_q(\delta)= 
\begin{cases} 0, &\mbox r\le\delta\le1 \\ 1-\delta/r, &\mbox{} 0\le\delta < r. \end{cases}
\end{equation*}
\end{theorem}

\begin{proof}[Sketch of proof]
First, consider the case of $r\le\delta\le1$.  Notice that we can apply the Plotkin bound directly, as $rn < \delta n = d$.  By the Plotkin Bound, $A_q(n,\delta n) \le \frac{\delta n}{\delta n - rn}$.  Cancelling
out the common $n$, we get $A_q(n,\delta n) \le \frac{\delta}{\delta - r}$.  Since this value is independent of $n$, it immediately follows from the definition that $\alpha_q(\delta)=0$.

Next, consider the case of $0\le\delta < r$.  Suppose that $\mathcal{C}$ is an $(n,M,\delta n)$ code where $M=A_q(n,\delta n)$ .  Our goal is to puncture $\mathcal{C}$ such that 
we get a shorter length code $\mathcal{C}'$ with the same minimum distance as $\mathcal{C}$.  The idea is to find a code whose $n$ is small enough that we can still apply the Plotkin bound, and then bound
our original code $\mathcal{C}$ with the shortened code's Plotkin value.
Use a shortening technique analgous to the one we described in lecture, as well as Section 1.5.3 of the textbook,
let $\mathcal{C}'$ be the $(n',M',\delta n)$ code where $n' = \lfloor (\delta n -1)/ r \rfloor$ and $M' \ge M/q^{n-n'}$.  Given this code, we can show that $A_q(n,\delta n) \le q^{n-n'} \delta n$.
Simplifying using the definition of $\alpha_q(\delta)$ completes the proof.
\end{proof}

Once again, we use MATLAB to visually compare two bounds.  This time, we consider the Asymptotic Singleton and Asymptotic Plotkin bounds.

\begin{figure}[ht]
\includegraphics[width=.8\linewidth]{asympt.png}
\caption{Asymptotic Plotkin and Singleton bounds for $q=2$}
\end{figure}

\section{Lexicodes}

We end our discussion on bounds with an interesting class of linear codes
called lexicodes, short for lexicographic codes.  Lexicodes are linear and meet the Gilbert bound; we will discuss the former and prove the latter.  Note that for this discussion we are 
solely working in $\mathbb{F}_2$.

We construct the lexicode $\mathcal{L}(n,d)$ of length $n$ and minimum distance $d$ using a basic greedy algorithm as follows.  First, order all $n$-tuples in an array $A$ in lexicographic order:
$A[0] = 0\cdots000$, $A[1]=0\cdots001$, $A[2]0\cdots010$, $A[3]=0\cdots011$, \ldots, $A[2^n-1] = 1\cdots111$.  Put the first vector from  $A$ (always the $\mathbf{0}$ vector) in $\mathcal{L}$.  Next, find the first vector $\mathbf{x}$
of weight $d$ in the lexicographic ordering, and put it in $\mathcal{L}$.  Then, find the next vector in the lexicographic ordering in $A$ whose distance from each vector in $\mathcal{L}$ is 
$d$ or more and add it to $\mathcal{L}$.  Repeat this process until you have scanned through all of $A$ once.

@@

\begin{enumerate}[{\normalfont (i)}]
\item $\mathcal{L}$ is a linear code and the vectors $\mathbf{c}_{2^i}$ are a basis of $\mathcal{L}$.  
\item After $\mathbf{c}_{2^i}$ is chosen, the next $2^i -1$ vectors can be rewritten as $\mathbf{c}_1 + \mathbf{c}_{2^i}$, $\mathbf{c}_2 + \mathbf{c}_{2^i}$, $\ldots$, 
$\mathbf{c}_{2^i -1} + \mathbf{c}_{2^i}$.
\item Let $\mathcal{L}_i = \{\mathbf{c}_0,\mathbf{c}_1,\ldots,\mathbf{c}_{2^i -1}\}$.  Then $\mathcal{L}_i$ is an $[n,i,d]$ linear code.

@@

I claim that (i) and (iii) follow from (ii).  For (ii), we are showing that all codewords in the lexicode are simply linear combinations of 
the $c_{2^i}$ codewords, hence making the $c_{2^i}$ codewords a basis for the code.  The sketch of the proof for (ii) involves inducting on $i$.  Essentially, the proof works
by assuming that the second $2^{i}$ vectors in $\mathcal{L}_{i+1}$ are not necessarily generated by adding $\mathbf{c}_2^{i}$ to each of the previously chosen vectors
in $\mathcal{L}_i$.  If you break this assumption, then you can use the notion of lexicographic order to find two vectors lexicographically ordered in a way that is not actually
possible.

@@

We now consider a basic example of a lexicode $\mathcal{L}(n,d)$ and it's $\mathcal{L}_{i}$s.

@@

@@

It may be surprising to discover that many codes we have already discussed in lecture are in fact lexicodes.  In order to have this discussion, though, we
first need two important definitions.

@@

We have used the idea of nim-sums and zero-sums throughout the course, but instead we have
used the terms even-like or odd-like.  In the binary case, these are equivalent notions.

We also need the following Lemma:

\begin{lemma}
The codewords of the lexicode $\mathcal{L}(n,d)$ are also in the lexicode $\mathcal{L}(n+1,d)$, except with an additional leading zero.
\end{lemma}

\begin{proof}
This follows directly from how our algorithm above was constructed.  We obviously have $\mathbb{F}_q^n \subset \mathbb{F}_q^{n+1}$, and in our algorithm these will be
the first $2^n$ vectors that are visited.  Since all that has changed is we've added a leading $0$, the algorithm will choose these same vectors $\mathcal{L}(n,d)$ vectors.
\end{proof}

In lecture, we have frequently discussed the code of all even-weight codewords.  In $\mathbb{F}_2$, this is a lexicode.

@@

\begin{proof}
We will prove this by inducting on $n$.  In the base case of $n=1$,
$\mathcal{L}=\{0\}$, which is trivially zero-sum.

Assume that, for the lexicode of length $n$, all codewords are zero-sum.  Now, we must show that all
the codewords in $\mathcal{L}(n+1,2)$ are zero-sum as well.  By our lemma, all codewords in $\mathcal{L}(n,2)$ are also in $\mathcal{L}(n+1,2)$, except with an
extra leading zero.  By our assumption, these codewords are still zero-sum, as adding a zero in front will not change the nim-sum calculation.

Let ${\mathbb{F}_q^n}^*$ be the vectors of $\mathbb{F}_q^n$ with a zero appended in front of the first coordinate.  Now, we must show that for the remaining vectors $v\in\mathbb{F}_q^{n+1} \setminus {\mathbb{F}_q^{n}}^*$that we have not yet visited, our algorithm will choose all
even-weight vectors and none of the odd-weight vectors.

First, consider the odd-weight vectors of $\mathbb{F}_q^{n+1} \setminus {\mathbb{F}_q^{n}}^*$.  Note that 
these are actually just the even weight vectors of $\mathbb{F}_q^n$ with a $1$ appended to the front.  If you flip the first bit of each vector, you get an even weight codeword that
we have already shown to be in $\mathcal{L}(n+1,2)$, and consequently no such odd-weight codeword can be in $\mathbb{L}(n+1,2)$.

Finally, consider the even-weight vectors of $\mathbb{F}_q^{n+1} \setminus {\mathbb{F}_q^{n}}^*$.  Notice that these are just the odd-weight vectors of $\mathbb{F}_q^n$ with a $1$
appended to the front.  By our assumption, none of the odd-weight vectors of ${\mathbb{F}_q^n}^*$ are in $\mathcal{L}(n+1,2)$.  This means that each even-weight
vector in $\mathbb{F}_q^{n+1} \setminus {\mathbb{F}_q^{n}}^*$ will necessarily have distance $2$ from vectors in $\mathcal{L}(n,2)$ (with a zero appended to the front).  We also
have that any two distinct even-weight vectors are at least distance $2$ from one another, as an even-weight vector can only possibly have distance one from an odd-weight vector.  
Hence, all even-weight vectors of $\mathbb{F}_q^{n+1} \setminus {\mathbb{F}_q^{n}}^*$ will be chosen by our algorithm.
\end{proof}

We have also frequently discussed the Hamming codes.  In (insert reference to Greedy Codes paper), they show that the binary lexicodes with $d$=3 and $n=2^m-1$ are the Hamming codes, 
and similarly, as one might expect considering the previous statement, the binary lexicodes with $d=4$ and $n=2^m$ are the extended Hamming codes.  We can check
this with a simple example.

\begin{exmp}
Let $n=7$, $d=3$.  It can be quite tedious to compute and confirm something like this by hand, so I wrote a short C++ program that implements the Lexicode algorithm as described above.  We find $\mathcal{L}(7,3)$ to be $\{0,7,25,30,42,45,51,52,75,76,82,85,97,102,120,127\}$ where the binary vectors are given by their decimal representation.
\end{exmp}

Note that $\mathcal{L}(7,3)$ has $16$ codewords, making it a $[7,4,3]$ code.  Recall that in lecture we proved that all $[7,4,3]$ codes are the Hamming(7,4) code.
